

\documentclass[12pt, a4paper]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{imakeidx}
\usepackage{geometry}
\usepackage{tfrupee}
\pagestyle{fancy}
\fancyhf{}
\rhead{Conic}
\lhead{Question Paper}
\rfoot{Page \thepage}
\lfoot{FWC}

\begin{document}
\title{\textbf Conic}
\maketitle \date
\begin{center} \textbf{12th Maths}\end{center}


\begin{enumerate}
\item Using integration, find the area of the region enclosed by the curve $ y=x^2 $, the x-axis and the ordinates $x=-2$ \text { and } $x=1$.
\begin{center}\textbf{OR}\end{center}

Using integration, find the area of the region enclosed by line $y=\sqrt{3}x$ semi-circle $y=\sqrt{4-x^2}$ and x-axis in first quadrant.


\item (a) Using integration, find the area of the smaller region enclosed by the curve ${4x^2 + 4y^2} = 9$ and the line $2x + 2y = 3$.
\begin{center}\textbf{OR}\end{center}

	(b) If the area of the regin bounded by the curve $y^2 = 4ax$ and the line $x = 4a$ is $\dfrac{256}{3}$\hspace{0.2cm} sq. units, then using integration, find the value of a, where $a>0$.


\item Find the area of the region enclosed by the curves $y^2=x$, $x=\dfrac{1}{4}$, $y=0$ and $x=1$, using integration.



\item If the area of the region bounded by the line $y=mx$ and the curve $x^2=y$ is $\dfrac{32}{3}$\hspace{0.2cm}sq. units, then find the positive value of m, using integration.


\item (a) Find the area bounded by the ellipse $x^2+4y^2=16$ and the ordinates $x=0$ and $x=2$, using integration.\begin{center}\textbf{OR}\end{center}


(b) Find the area of the region $\{(x,y): x^2 \leq y \leq x\}$, using integration.


\item The slope of the normal to the curve $y = 2x^2+3 sin x$ at $x=0$ is \underline{\hspace{1cm}}.\begin{center}\textbf{OR}\end{center}

The total revenue (in \rupee) received from sale of x units of a product is $R(x) = 3x^2 + 36x + 5$. The marginal revenue, when $x=12$ is \underline{\hspace{1cm}}.


\item Find the equation of tangent to the curve $y = x^2 + 4x + 1$ at the point $(3,22)$.


\item If the area between the curves  $x = y^2$ and $x = 4$ is divided into two equal parts by the line $x = a$, then find the value of a, using integration. \begin{center}\textbf{OR}\end{center}
Find : 
\\$$\int \dfrac {x}{(x-1)^2 (x+2)}dx$$



\end{enumerate}		

\end{document}









